Forschungsprojekt

### 2020-10-16 documentation/presentation/main.tex
dinge

\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{tikz}
\usetikzlibrary{positioning}

@@

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Introduction}
\begin{center}
	\begin{minipage}{0.6\linewidth}
		\centering
		Main Goal: \itshape  Comparison of five graph processing systems in their performance on different graphs and algorithms.
	\end{minipage}
\end{center}

\begin{enumerate}
	\item Preliminaries
	\begin{itemize}
	\item Basics
	\item Computation Styles
	\item Hugepages
	\end{itemize}
	\item Frameworks
	\item Evaluation
	\begin{itemize}
	\item Research vs. Production Case
	\item Results
	\item Impact of Hugepages on Galois
	\end{itemize}
	\item Conclusion
\end{enumerate}

@@

		\node at (2.5,3) {$w(x)=1\ \forall x\in V$};
	\end{tikzpicture}
	\end{center}
	\columnbreak
	\subsection*{Algorithms}
	\begin{description}
		\item[Single-Source Shortest-Paths (SSSP):] find the shortest path from a starting vertex to every other vertex

@@

	\draw[->, line width=1pt] (a) edge node[midway, above] {1} (b);
	\draw[->, line width=1pt] (a) edge node[midway, above] {1} (c);
	\draw[->, line width=1pt] (a) edge node[midway, right] {1} (d);
\end{tikzpicture}
\end{center}
\begin{itemize}
	\item reads active vertex, writes neighborhood 
	\item more efficient, if only few active vertices at the same time
	\item more efficient, if neighborhoods do not overlap
\end{itemize}

@@

\section{Hugepages}
\begin{itemize}
	\item most systems use virtual memory management
\begin{itemize}
	\item represents an abstraction to hardware memory
	\item virtual memory is then organized in pages
	\item translations of virtual memory to physical memory are cached, because every translation takes time
\end{itemize}
	\item typically, memory pages are 4 KiB in size
	\item \textbf{hugepages} can be several MiB in size $\rightarrow$ reduce number of cache misses
	\item especially noticeable in very memory intensive applications
\end{itemize}

\section{Frameworks}

@@

\begin{multicols}{2}
\begin{description}
	\item[$\color{Galois}\blacksquare$ Galois] is a general purpose library designed for parallel programming
	\begin{itemize}
		\item Version 6.0 from 29\textsuperscript{th} June 2020 used 
	\end{itemize}
	\item[$\color{Gemini}\blacksquare$ Gemini] uses a distributed message-based approach from scratch
	\begin{itemize}
		\item Version from 2\textsuperscript{nd} November 2016 used
		\item Version contains bugs that had to be fixed 
	\end{itemize}

	\item[$\color{Giraph}\blacksquare$ Giraph] is built on Apache Hadoop, a large scale data processing infrastructure
	\begin{itemize}
		\item Version 1.3 from 8\textsuperscript{th} May 2020 used
		\item BFS is not natively supported 
		\item state-of-the-art, but not NUMA-aware
	\end{itemize}
	\item[$\color{Ligra}\blacksquare$ Ligra] dynamically switches between push and pull style
	\begin{itemize}
		\item Version from 14\textsuperscript{th} August 2019
	\end{itemize}
	\item[$\color{Polymer}\blacksquare$ Polymer] optimizes data layout and memory access strategies
	\begin{itemize}
		\item Version from 28\textsuperscript{th} August 2018
	\end{itemize}
\end{description}
\end{multicols}

@@

\subsection*{Graphs}
Both rMat graphs are synthetic, others are real-world data sets
\begin{center}
	\includegraphics[width=\linewidth]{graphsize.png}
\end{center}

\end{multicols}

\clearpage
\begin{multicols}{2}
\section{Production Case}
\begin{itemize}
	\item running system: multiple calculations on a single graph
	\item graph data stays loaded between calculations
	\item[$\rightarrow$] short calculation times should be preferred
\end{itemize}

\columnbreak
\section{Research Case}
\begin{itemize}
	\item individual calculation cases: possibly new graph for each calculation
	\item frequently changing algorithm
	\item[$\rightarrow$] framework should be relatively fast on different algorithms
	\item[$\rightarrow$] overall small execution times should be preferred
\end{itemize}
\end{multicols}

\section{Production Case Single Node}

\begin{figure}[h]
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{SSSP}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
		\caption{BFS}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodePR_calcTime.png}
		\caption{PR}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Giraph is either very slow or requires too much RAM (>256 GB)
	\item On SSSP, Polymer is fastest, followed by Gemini on second place
	\item On BFS, Gemini and Ligra are comparable and fastest on the larger graphs
	\item On PR, Galois is fastest. But we exclude Galois Push because of possible measuring errors.
	\item Message-based approach can compete with shared-memory
\end{itemize}

@@

\begin{figure}[h]
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{SSSP}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_calcTime.png}
		\caption{BFS}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedPR_calcTime.png}
		\caption{PR}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Giraph is fastest on SSSP and BFS on the real world graphs
	\item Giraph has problems with synthetic graphs
	\item Gemini is fastest on PR, with Giraph on second place
\end{itemize}

@@

\begin{figure}[h]
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{SSSP}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_execTime.png}
		\caption{BFS}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodePR_execTime.png}
		\caption{PR}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Giraph is either slowest or requires too much RAM (>256 GB)
	\item Galois is fastest in almost all cases, second fastest is Ligra
	\item Gemini and Polymer are comparably slow
\end{itemize}

@@

\begin{figure}[h]
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{SSSP}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_execTime.png}
		\caption{BFS}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedPR_execTime.png}
		\caption{PR}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Galois Push is faster than Pull in all cases
	\item Either Galois implementation is faster than any other frameworks on SSSP or BFS
	\item Gemini is fastest on PR and comparable to Giraph on SSSP and BFS
\end{itemize}

\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=1cm, right=1cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Galois With Hugepages on SSSP}
\begin{figure}[h!]
\hfil
\begin{subfigure}{0.33\linewidth}
	\sffamily
	\small
	\centering
	\begin{tabular}{cr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}
		&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{2-3}\cmidrule{4-5}
		\bf Graph&w/o&w/&w/o&w/\\
		\midrule
		flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5\\
		wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1\\
		twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1\\
		rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4\\
		friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5\\
		rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1\\
\end{tabular}
\end{subfigure}
\hfil
\begin{subfigure}{0.3\linewidth}
\centering
\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisThreads.png}
	\caption{Without Hugepages}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}
\centering
\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
	\caption{With Hugepages}
\end{subfigure}
\end{figure}
\begin{itemize}
	\item Hugepages further reduce both calculation and execution time
	\item Speedups with hugepages are \enquote{more reliable}, i.e., more predictable
\end{itemize}

\section{Galois With Hugepages on PR Pull}
\begin{figure}[h!]
\hfil
\begin{subfigure}{0.33\linewidth}
	\sffamily
	\small
	\centering
	\begin{tabular}{cr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
		&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{2-3}\cmidrule{4-5}
		\bf Graph&w/o&w/&w/o&w/\\
		\midrule
		flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6\\
		wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4\\
		twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3\\
		rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1\\
		friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1\\
		rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4\\
\end{tabular}
\end{subfigure}
\hfil
	\begin{subfigure}{0.3\linewidth}
	\centering
\includegraphics[width=\linewidth]{../../plots/singleNodePRPullGaloisThreads.png}
		\caption{Without Hugepages}
\end{subfigure}
\begin{subfigure}{0.3\linewidth}
	\centering
\includegraphics[width=\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
		\caption{With Hugepages}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Hugepages further reduce both calculation and execution time
	\item Hugepages make speedup in multithreaded scenario possible
	\item Speedup not to the same degree as with SSSP (15$\times$ vs. 2.5$\times$)
\end{itemize}

@@

2) single node almost always preferrable, as long as RAM is sufficient
\begin{multicols}{2}
	\subsection{Production Case}
	\begin{itemize}
		\item Giraph is very fast on distributed systems (especially SSSP and BFS), with added benefit of Hadoop (fault-tolerance, automatic parallelization) 
		\item Gemini (surprisingly) and Ligra are good options for single node 
	\end{itemize}

@@

\subsection{Outlook}
\begin{itemize}
	\item[$\rightarrow$] incorporate new frameworks and new algorithms
	\item[$\rightarrow$] explore range of settings and other implementations
	\item[$\rightarrow$] repeat similar tests in the future: frameworks are improved and new ones are introduced
\end{itemize}

>>>>

\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{positioning}

\definecolor{heading}{HTML}{002d57}

\usepackage[pages=all]{background}

\backgroundsetup{
scale=1,
color=black,
opacity=0.4,
angle=0,
contents={%
	\includegraphics{background.pdf}
  }%
}

@@

\newcommand{\todo}[1]{{\color{red}#1}}

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Motivation and Goal}
\sffamily
\begin{center}

	\vfill

	\begin{itemize}
		\item graph processing becomes increasingly important in academic and industrial environments
		\item many problems modeled with graphs, e.\,g.,\xspace machine learning and data mining
		\item many business models are based on graphs, e.\,g.,\xspace viral marketing or Google’s search engine
		\item graph sizes increase to several billion edges 
		\item[$\rightarrow$] performance, parallelism and distribution of graph algorithms becomes more important
	\end{itemize}

	\vfill

	\begin{minipage}{0.6\linewidth}
		\centering
		Main Goal: \itshape  Comparison of five graph processing systems in their performance on different graphs and algorithms.
	\end{minipage}

	\vfill
\end{center}

\section{Overview}
\vfill
\begin{enumerate}
	\item Preliminaries
	\begin{itemize}
	\item Basics
	\item Computation Styles
	\item Hugepages
	\end{itemize}
	\item Frameworks
	\item Evaluation
	\begin{itemize}
	\item Research vs. Production Case
	\item Results
	\item Impact of Hugepages on Galois
	\end{itemize}
	\item Conclusion
\end{enumerate}
\vfill

@@

		\node at (2.5,3) {$w(x)=1\ \forall x\in E$};
	\end{tikzpicture}
	\end{center}
	\columnbreak
	\subsection*{Algorithms}
	\begin{description}
		\item[Single-Source Shortest-Paths (SSSP):] find the shortest path from a starting vertex to every other vertex

@@

	\draw[->, line width=1pt] (a) edge node[midway, above] {1} (b);
	\draw[->, line width=1pt] (a) edge node[midway, above] {1} (c);
	\draw[->, line width=1pt] (a) edge node[midway, right] {1} (d);
\end{tikzpicture}
\end{center}
\begin{itemize}
	\item reads active vertex, writes neighborhood 
	\item more efficient, if only few active vertices at the same time
	\item more efficient, if neighborhoods of active vertices do not overlap
\end{itemize}

@@

\section{Hugepages}
\vspace{2cm}
\begin{itemize}
	\item most systems use virtual memory management
\begin{itemize}
	\item represents an abstraction to hardware memory
	\item virtual memory is organized in pages
	\item translations of virtual memory to physical memory are cached, because every translation takes time
\end{itemize}
	\item typically, memory pages are 4 KiB in size
	\item \textbf{hugepages} can be several MiB in size $\rightarrow$ reduce number of cache misses
	\item especially noticeable in very memory intensive applications
\end{itemize}

% \section{Frameworks}

@@

% \begin{multicols}{2}
% \begin{description}
% 	\item[$\color{Galois}\blacksquare$ Galois] is a general purpose library designed for parallel programming
% 	\begin{itemize}
% 		\item Version 6.0 from 29\textsuperscript{th} June 2020 used 
% 	\end{itemize}
% 	\item[$\color{Gemini}\blacksquare$ Gemini] uses a distributed message-based approach from scratch
% 	\begin{itemize}
% 		\item Version from 2\textsuperscript{nd} November 2016 used
% 		\item Version contains bugs that had to be fixed 
% 	\end{itemize}

% 	\columnbreak

% 	\item[$\color{Giraph}\blacksquare$ Giraph] is built on Apache Hadoop, a large scale data processing infrastructure
% 	\begin{itemize}
% 		\item Version 1.3 from 8\textsuperscript{th} May 2020 used
% 		\item BFS is not natively supported 
% 		\item state-of-the-art, but not NUMA-aware
% 	\end{itemize}
% 	\item[$\color{Ligra}\blacksquare$ Ligra] dynamically switches between push and pull style
% 	\begin{itemize}
% 		\item Version from 14\textsuperscript{th} August 2019
% 	\end{itemize}
% 	\item[$\color{Polymer}\blacksquare$ Polymer] optimizes data layout and memory access strategies
% 	\begin{itemize}
% 		\item Version from 28\textsuperscript{th} August 2018
% 	\end{itemize}
% \end{description}
% \end{multicols}

% Features, version, numa, message passing/sharememory, bfs fehlt?

\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=2cm, right=2cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Frameworks}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccp{8cm}p{6cm}}
	Framework&Version&NUMA&Dist.&\multicolumn{1}{c}{Features}&\multicolumn{1}{c}{Notes}\\
	\toprule
	$\color{Galois}\blacksquare$\ \bf Galois&29.06.2020&\checkmark&(\checkmark)&general purpose library designed for parallel programming&Distributed using Gluon\\\midrule
	$\color{Gemini}\blacksquare$\ \bf Gemini&02.11.2016&\checkmark&\checkmark&distributed message-based approach from scratch&Version contains bugs that had to be fixed \\\midrule
	$\color{Giraph}\blacksquare$\ \bf Giraph&08.05.2020&X&\checkmark&built on Apache Hadoop&BFS is not natively supported \\\midrule
	$\color{Ligra}\blacksquare$\ \bf Ligra&14.08.2019&\checkmark&X&dynamically switches between push and pull style&\\\midrule
	$\color{Polymer}\blacksquare$\ \bf Polymer&28.08.2018&\checkmark&X&optimizes data layout and memory access strategies&\\
\end{tabular}

@@

\subsection*{Graphs}
Both rMat graphs are synthetic, others are real-world data sets; Flickr: 24MB, rMat28: 76GB%
\begin{center}
	\includegraphics[width=\linewidth]{graphsize.png}
\end{center}
\end{multicols}

\begin{multicols}{2}
\section{Production Case}
\vspace{1cm}
\begin{itemize}
	\item running system: multiple calculations on a single graph
	\item graph data stays loaded between calculations
	\item[$\rightarrow$] short calculation times should be preferred
	\item Not main focus of this presentation!\footnote{\sffamily see paper for details}
\end{itemize}

\columnbreak
\section{Research Case}
\vspace{1cm}
\begin{itemize}
	\item individual calculation cases: possibly new graph for each calculation
	\item frequently changing algorithm
	\item[$\rightarrow$] framework should be relatively fast on different algorithms
	\item[$\rightarrow$] overall small execution times should be preferred
\end{itemize}
\end{multicols}

% \section{Production Case Single Node}

% \begin{figure}[h]
% 	\begin{subfigure}{0.32\textwidth}
% 		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
% 		\caption{SSSP}
% 	\end{subfigure}
% 	\begin{subfigure}{0.32\textwidth}
% 		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
% 		\caption{BFS}
% 	\end{subfigure}
% 	\begin{subfigure}{0.32\textwidth}
% 		\includegraphics[width=\linewidth]{../../plots/singleNodePR_calcTime.png}
% 		\caption{PR}
% 	\end{subfigure}
% \end{figure}
% \begin{itemize}
% 	\item Giraph is either very slow or requires too much RAM (>256 GB)
% 	\item On SSSP, Polymer is fastest, followed by Gemini on second place
% 	\item On BFS, Gemini and Ligra are comparable and fastest on the larger graphs
% 	\item On PR, Galois Pull is fastest, we exclude Galois Push because of possible measuring errors.
% 	\item \todo{Message-based approach can compete with shared-memory}
% \end{itemize}
% \todo{Grafiken Größer?}

@@

\begin{figure}[h]
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{SSSP}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedPR_calcTime.png}
		\caption{PR}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Giraph is fastest on SSSP and BFS on the real world graphs
	\item Giraph has problems with synthetic graphs
	\item Gemini is fastest on PR, with Giraph on second place
\end{itemize}

@@

\begin{figure}[h]
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{SSSP}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodePR_execTime.png}
		\caption{PR}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Giraph is either slowest or requires too much RAM (>256 GB)
	\item Galois is fastest in almost all cases, second fastest is Ligra
	\item Gemini and Polymer are comparably slow
\end{itemize}

@@

\begin{figure}[h]
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{SSSP}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedPR_execTime.png}
		\caption{PR}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Galois Push is faster than Pull in all cases
	\item Both Galois implementations fastest on SSSP or BFS
	\item Gemini is fastest on PR in almost all cases
\end{itemize}

%\newgeometry{paperwidth=28.1cm, paperheight=18cm, left=1cm, right=1cm, top=0.7cm,bottom=1cm,includefoot,heightrounded}
\section{Galois With Hugepages}
\begin{figure}[h!]
\begin{subfigure}{0.4\textwidth}
	\sffamily
	\small
	\centering
	\begin{tabular}{cr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}
		&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{2-3}\cmidrule{4-5}
		\bf Graph&w/o&w/&w/o&w/\\
		\midrule
		flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5\\
		wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1\\
		twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1\\
		rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4\\
		friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5\\
		rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1\\
\end{tabular}
\caption{SSSP}
\end{subfigure}
\hfil
\begin{subfigure}{0.4\textwidth}
\sffamily
\small
\centering
\begin{tabular}{cr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
		&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{2-3}\cmidrule{4-5}
		\bf Graph&w/o&w/&w/o&w/\\
		\midrule
		flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6\\
		wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4\\
		twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3\\
		rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1\\
		friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1\\
		rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4\\
\end{tabular}
\caption{PR Pull}
\end{subfigure}
\end{figure}
\vfill
\begin{itemize}
	\item Hugepages reduce both calculation and execution time on all algorithms
	\item[$\rightarrow$] Execution times can be up to 3$\times$ shorter
\end{itemize}
\vfill

\section{Multithreaded Speedup of Galois}
\begin{figure}[h!]
\begin{subfigure}{0.45\textwidth}
	\centering
\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
\caption{SSSP with Hugepages}
\end{subfigure}
\hfil
\begin{subfigure}{0.45\textwidth}
	\centering
\includegraphics[width=\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
		\caption{PR Pull with Hugepages}
	\end{subfigure}
\end{figure}
\begin{itemize}
	\item Speedups can be significant, with and without hugepages
	\item Speedup of PR not to the same degree as on SSSP (2.5$\times$ vs. 15$\times$)
\end{itemize}

@@

2) single node almost always preferrable, as long as RAM is sufficient
\begin{multicols}{2}
	\subsection{Production Case}
	\begin{itemize}
		\item Giraph is very fast on distributed systems (especially SSSP and BFS)
		\item Gemini and Ligra are good options for single node 
	\end{itemize}

@@

\subsection{Outlook}
\begin{itemize}
	\item[$\rightarrow$] incorporate new frameworks and new algorithms
	\item[$\rightarrow$] explore range of settings and other implementations
	\item[$\rightarrow$] repeat similar tests in the future: frameworks are updated and new ones are introduced
\end{itemize}
